%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000


\begin{minipage}[t]{.95\textwidth} % The left column takes up 33% of the text width of the page
\large
Dear Hiring Manager,
\vspace{10pt}\\
I am writing to express my interest in the Full Stack Engineer Position. I am a 4th year at UCLA expected to graduate June 2020 with a Bachelor of Sciences in Computer Science. My academic and work experience have familiarized me with C/C++, Python, Java, and JavaScript development in projects ranging from small modules to full-stack development. I feel I am a strong candidate.
\vspace{6pt}\\
I am excited by the challenges and elegant solutions that Software Engineering presents. My pursuit of problem solving using Software Engineering began in highschool working for Ondas Networks Inc. (then Full Spectrum Inc.). Faced with part tracking inconsistencies, I developed a solution using SQL and PHP. Studying Computer Science in a formal setting reinforced my interest in software development. Bolstered by completing courses such as Algorithms, Programming Languages, and Networking, I attacked a variety of problems. Developing software for the UCLA ELFIN CubeSat Project, I employed a pair of Python servers to simplify the interaction between multiple software suites. To enable operator interaction, I completed the stack with a QT GUI capable of managing both servers. At Boeing, I proposed using NLP techniques to compare enterprise processes for equivalence. The doc2vec solution I developed had the potential to greatly reduce the manual effort required to map data between processes.
\vspace{6pt}\\
Throughout all the projects and languages I have faced, I am always excited by the potential Software Engineering solutions. I am eager to continue learning and tackle new problems. I feel this makes me a strong candidate for the Full Stack Engineer Position.
\vspace{22pt}\\
Best Regards,
\vspace{15pt}\\
Graham Wing


\end{minipage} % The end of the right column
% \vspace*{\fill}